PAGAI : a path sensitive static analyser

### 2012-05-22 papers/TAPAS2012/pagai.tex

\documentclass{entcs} 
\usepackage{entcsmacro}
\usepackage{ifxetex}
\ifxetex
\else
\usepackage[utf8]{inputenc}
\fi

@@

\begin{figure}[!h]
\begin{minipage}[c]{.49\linewidth}
\begin{C}
int x = 0;
int t = 0;
int phase = 0;

while (t < 100) {
   if (phase == 0) 
      x = x+2;
   if (phase == 1) 
      x = x-1;
   phase = 1-phase;
   t++;
}
assert(x <= 100);
\end{C}
\end{minipage}
\begin{minipage}[c]{.49\linewidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=1.5cm,
                    semithick,font=\footnotesize]

@@

>>>>

\documentclass{entcs} 
\usepackage{entcsmacro}

\usepackage{ifxetex}
\ifxetex
\else
\usepackage[utf8]{inputenc}
\fi

@@

\begin{figure}[!h]
\begin{minipage}[c]{.35\linewidth}
\begin{C}
int x = 0;
int t = 0;
int phase = 0;

while (t < 100) {
   if (phase == 0) 
      x = x+2;
   if (phase == 1) 
      x = x-1;
   phase = 1-phase;
   t++;
}
assert(x <= 100);
\end{C}
\end{minipage}
\begin{minipage}[c]{.64\linewidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=1.5cm,
                    semithick,font=\footnotesize]

@@

It is not totally relevant to compare by inclusion the abstract values obtained
by the various analysis techniques. Indeed, a slightly smaller invariant may not
always be useful to prove the desired properties.
A future work is thus to experiment with
better comparison metrics, such as:
\begin{itemize}
	\item the number of \emph{assert} that have been proved in the code.
		Unfortunately, it is difficult to find good benchmarks or real life
		programs with many \emph{assert} statements.
	\item the number of false alarms in a client analysis that detects array
		bound violations, arithmetic overflows, etc.
\end{itemize}
